Full Title

### 2018-01-21 cones/paper/cones.tex
More changes.

Recall that we start with an oplax symmetric monoidal functor $j\from \C'\to\C$.  
The objects of $C_j$ are the objects of $\C$.  
Given objects $A,B$ of $\C$, the class of morphisms $A\to B$ is given by the colimit of the functor
\[
  \oppcat{\C'} \xrightarrow{\oppcat{j}}
  \oppcat{\C} \xrightarrow{\C[\blank\tensor A,B]}
  \Set\,.
  \]
That is, a morphism from $A$ to $B$ is a pair $(X,f)$, where $X$ is an object of $\C'$ and $f\from jX \tensor A \to B$ is a morphism in $\C$.  
Furthermore, $(X, f)$ and $(X', f')$ are considered to be equivalent if there is some morphism $h\from X'\to X$ in $\C'$ making the following diagram commute:
\[
  \begin{tikzcd}
    j X' \tensor A \arrow[r, "f'"] \arrow[d, "j h \tensor A"']
      & B \\
    j X \tensor A \arrow[ur, "f"']
      &
  \end{tikzcd}\,.
  \]
Given morphisms $(X,f)\from A \to B$, $(Y,g)\from B \to C$, the composite is given by $(Y\tensor X,f;g)$, where $f;g$ is the following composite in $\C$:
\begin{align*}
  j(Y\tensor X)\tensor A & \xrightarrow{m_j\tensor A}
    (jY \tensor jX) \tensor A \\ & \xrightarrow{\assoc}
      jY \tensor (jX \tensor A) \\ & \xrightarrow{jY \tensor f}
        jY \tensor B \xrightarrow{g}
          C\,.
\end{align*}
We can prove that this composition is associative using the usual coherence theorems for monoidal categories.  
Similarly, the symmetric monoidal structure from $\C$ induces a symmetric monoidal structure on $C_j$.

@@

A consequence of the initiality of the cone construction is that it is \emph{functorial}; that is, given a square of the following form:
\[
  \begin{tikzcd}[row sep=large, column sep=large]
    \C' \arrow[r, "F", ""'{name=term}] \arrow[d, "j"']
      & \D' \arrow[d, "j'"] \\
    \C \arrow[r, "G"', ""{name=J}]
      & \D
    \arrow[Rightarrow, from=term, to=J, "\psi"]
  \end{tikzcd}\,,
  \]
where horizontal arrows correspond to lax monoidal functors and vertical arrows to monoidal functors, we get an induced lax monoidal functor $C_{j}\to C_{j}$, in a way that respects horizontal pasting of squares.

@@

In order to model \emph{countable} nondeterminism, rather than arbitrary nondeterminism, we want to constrain our model so that

>>>>

Recall that we start with an oplax symmetric monoidal functor $j\from \C'\to\C$.  
The objects of $C_j$ are the objects of $\C$.  
Given objects $A,B$ of $\C$, the class of morphisms $A\to B$ is given by the colimit of the functor
\[
  \oppcat{\C'} \xrightarrow{\oppcat{j}}
  \oppcat{\C} \xrightarrow{\C[\blank\tensor A,B]}
  \Set\,.
  \]
That is, a morphism from $A$ to $B$ is a pair $(X,f)$, where $X$ is an object of $\C'$ and $f\from jX \tensor A \to B$ is a morphism in $\C$.  
Furthermore, $(X, f)$ and $(X', f')$ are considered to be equivalent if there is some morphism $h\from X'\to X$ in $\C'$ making the following diagram commute:
\[
  \begin{tikzcd}
    j X' \tensor A \arrow[r, "f'"] \arrow[d, "j h \tensor A"']
      & B \\
    j X \tensor A \arrow[ur, "f"']
      &
  \end{tikzcd}\,.
  \]
Given morphisms $(X,f)\from A \to B$, $(Y,g)\from B \to C$, the composite is given by $(Y\tensor X,f;g)$, where $f;g$ is the following composite in $\C$:
\begin{align*}
  j(Y\tensor X)\tensor A & \xrightarrow{m_j\tensor A}
    (jY \tensor jX) \tensor A \\ & \xrightarrow{\assoc}
      jY \tensor (jX \tensor A) \\ & \xrightarrow{jY \tensor f}
        jY \tensor B \xrightarrow{g}
          C\,.
\end{align*}
We can prove that this composition is associative using the usual coherence theorems for monoidal categories.  
Similarly, the symmetric monoidal structure from $\C$ induces a symmetric monoidal structure on $C_j$.  
If $\C$ is symmetric monoidal \emph{closed}, then so is $C_j$.

@@

A consequence of the initiality of the cone construction is that it is \emph{functorial}; that is, given a square of the following form:
\[
  \begin{tikzcd}[row sep=large, column sep=large]
    \C' \arrow[r, "F", ""'{name=term}] \arrow[d, "j"']
      & \D' \arrow[d, "j'"] \\
    \C \arrow[r, "G"', ""{name=J}]
      & \D
    \arrow[Rightarrow, from=term, to=J, "\psi"]
  \end{tikzcd}\,,
  \]
where horizontal arrows correspond to lax monoidal functors and vertical arrows to monoidal functors, we get an induced lax monoidal functor $C_{j}\to C_{j}$, in a way that respects horizontal pasting of squares.
In particular, if $\C$ and $\C'$ have linear structures, compatible with $j$, then $C_j$ inherits a linear structure.

@@

We now restrict our attention to the inclusion functor $j\from G_{sw,rec}\hookrightarrow \G_{rec}$.  
Then $C_j$ inherits a linear structure from $\G_{rec}$.

\subsection{Extensional order}

Let $\sigma,\tau\from I \to \bN$ be morphisms in $C_j$, corrseponding to morphisms $\sigma'\from jX \to \bN$, $\tau'\from jY \to \bN$ in $\G_{rec}$.  
We say that $\sigma\lst\tau$ if the following two conditions hold:
\begin{itemize}
  \item If there exists $s\in \sigma'$ such that $s\vert_{\bN}=qn$, then there exists $t\in\tau'$ such that $t\vert_{\bN}=qn$.
  \item If $\sigma'$ is winning then $\tau'$ is winning.
\end{itemize}
In general, given strategies $\sigma,\tau\from I \to A$ in $C_j$, we say that $\sigma\lst\tau$ if for all morphisms $\rho\from A \to \bN$ we have $\sigma;\rho\lst\tau;\rho$.

We can show that this is well-defined; i.e., that it respects the equivalence relation we have already defined on morphisms.  
This is a good exercise to show the importance of surjective and winning strategies to our model.

\subsection{Countable nondeterminism}

In order to model \emph{countable} nondeterminism, rather than arbitrary nondeterminism, we want to constrain our model so that morphisms are strategies for $\oc\bN\tensor A \to B$, rather than $X \tensor A \to B$ for an arbitrary game $X$.

Since $\oc\bN$ has the structure of a comonoid, it gives rise to an oplax monoidal functor
\[
  n\from I \to \G_{rec}\,,
  \]
where $I$ is the one-object monoidal category.  
Moreover, this functor is linear distributive from the trivial linear structure on $I$ on to $\G$.
The cone $C_n$ is therefore a linear category.

Since $\G_{sw,rec}$ is a sub-linear category of $\G_{rec}$, the functor $n$ factors through a functor $n'\from I \to \G_{rec}$.  
By initiality of the cone construction, this gives rise to a functor $C_n\to C_j$.  
Our model of nondeterministic PCF will be the category $\C$ that is the image of this functor.
A morphism in $\C$ from a game $A$ to a game $B$ will be a strategy for $\oc \bN \tensor A \to B$, but the equivalence relation on morphisms is that from $C_j$.  
For example, two morphisms $f,g\from \oc\bN\to A$ are equivalent in $\C$ if there is a surjective winning strategy $\oc\bN\to \oc\bN$ commuting with $f$ and $g$, but they are not equivalent in $C_n$.

In fact, once we have applied the extensional quotient, there is no difference between working in $\C$ and working in $C_n$.  
We will use $\C$, because it is closer to being a fully abstract model for nondeterministic PCF before we apply the extensional quotient.

\subsection{The denotation of a term}

Let $M=C[\wn]\from T$ be a term of nondeterministic PCF, where $C[-]$ is a PCF context (i.e., a context not mentioning the constant $\wn$).  
Then the denotation of $M$ in $\C$ is given by the following composite:
\[
  I \xrightarrow{\phi_{\oc\bN}}
  \oc \bN \xrightarrow{J (\deno{\lambda n. C[n]})}
  \deno{T}
  \]
In other words, when considered as a morphism in $\G_{rec}$, $\deno{M}$ is precisely the denotation of the term $\lambda n.C[n]$ in $\G_{rec}$.

\subsection{Relation to our previous model}

Since our Harmer-McCusker-style model $\G_{ND}$
